---
title: "Credit Analysis"
output: github_document
editor_options: 
  chunk_output_type: console
---
# Introduction
This project aims to evaluate the creditworthiness of individuals by analyzing various financial and demographic factors. By leveraging statistical techniques and machine learning models, the analysis seeks to identify patterns and predictors of credit risk, helping lenders make informed decisions.

# Data Exploration/Insights and Interpretation

So, first, let's see the head of our data.

```{r setup, include=FALSE, eval=TRUE}
# Imports
library(tidyverse)
library(knitr)

# Loading data
data <- read.csv('../data/cleaned/credit.csv')
```

```{r include=TRUE}
# Showing data head
knitr::kable(head(data), 'pipe')
```

In this dataset, we can see various information about the bank's customers, such as their age, gender, education, how many children they have, marital status, their monthly earnings and expenses, how long the customer has been affiliated with the bank and, our target feature, how much is your credit limit on the card.

To make it possible to understand what affects the credit limit, let's study some variables and their behavior when correlated with our future 'output'. To begin with, let's evaluate the categorical variables.

## Marital Status

```{r include=FALSE, eval=TRUE}
# Verifying correlation between categorical data and Credit.Limit
plot_categorical_data_with_cl <- function(data, column.name, color) {
  return(
    ggplot(data, aes(x = !!sym(column.name), y = Credit.Limit)) +
      geom_boxplot() +
      scale_y_continuous(labels = scales::comma) +
      theme_classic() +
      labs(
        title = sprintf('Credit limit distribution for %s', column.name),
        subtitle = sprintf('How %s impacts credit limit', column.name),
        caption = 'Data source: EBAC Online Courses',
        x = column.name,
        y = 'Credit Limit'
      )
  )
}

# Verifying correlation between continuous data and Credit.Limit
plot_continuous_data_with_cl <- function(data, column.name, color) {
  return(
    ggplot(data) +
      geom_bar(aes(x=.data[[column.name]], y=Credit.Limit), stat = 'identity', fill = color) +
      scale_y_continuous(labels = scales::comma) +
      theme_classic() +
      labs(
        title = sprintf('Credit limit distribution for %s', column.name),
        subtitle = sprintf('How %s impacts in credit limit', column.name),
        caption = 'Data font: EBAC Online Courses',
        y = 'Credit Limit',
      )
  )
}
```

```{r include=TRUE}
# Showing data head
plot_categorical_data_with_cl(data, 'Marital.Status', 'gray75')
```

## Education

```{r include=TRUE}
# Showing data head
plot_categorical_data_with_cl(data, 'Education', 'gray75')
```

Now, we're gonna do the same rational, but with our continuous variables.

## Dependents

```{r include=TRUE}
# Showing data head
plot_continuous_data_with_cl(data, 'Dependents', 'gray75')
```

(In the future, change it to correlation map with the continuous data)





